Because different HPC system have different software and hardware configurations, configuring and building before running HPC application is necessary. However, it can take a lot of time and effort for application users and requires application users to have enough application technical knowledge.   Also, when users want to run legacy application developed years or even decades ago, required dependency libraries maybe hard to find or have difficulties compatible with current software stack. So, having a consistent execution environment across HPC system in different locations or time is desirable, however it is usually hard to accomplish on bare metal hosts. Container technology like Docker brings great benefits to application's development, build and deployment process. While most cloud computing systems are already equipped with Docker, not much work has been done to deploy Docker on HPC systems. In this work, we propose a Docker-enable build and execution environment for HPC system -- \texttt{BEE}. It brings all the benefits of Docker to existing HPC machines without installing software and with no system administrator configuration. We show that current HPC application can be easily configured to run BEE. It eliminates the need for reconfigure and rebuild applications for different systems and it also provides comparable performance. 

%Also, when a HPC system is shared between users and each user gets limited time slots, which is usually not enough to finish their computation process. This requires them to implement checkpoint/restoration feature, so that they can resume work when resources are available. However, these kind of checkpoint cannot be easily migrate to other available machines.